An Adaptive Algorithm Employing Continuous Linear Functionals

### 2019-01-02 AutoAlgorithmLinearFunctionalDataVerD.tex
New version after first submission.  Caught some typos.

To prove this, let $A^*$ be an arbitrary algorithm in $\calA(\calB_{\rho})$, and let $L_1, \ldots, L_N$ be the linear functionals chosen when evaluating this algorithm for the zero function with tolerance $\varepsilon$.  Thus, $A^*(0,\varepsilon)$ is some function of $(L_1(0) , \ldots, L_N(0)) = (0, \ldots, 0)$.  Let $f$ be a linear combination of $u_1, \ldots, u_{N+1}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_N(f) = 0$, then $A^*(\pm f) = A^*(0)$, and
\begin{align*}
\varepsilon & \ge \max_{\pm} \DHJRnorm[\calG]{S(\pm f) - A^*(\pm f)} =  \max_{\pm} \DHJRnorm[\calG]{\pm S( f) - A^*(0)} \\
& \ge \frac 12 \left [ \DHJRnorm[\calG]{S( f) - A^*(0)} + \DHJRnorm[\calG]{- S( f) - A^*(0)}\right] \\
& \ge \DHJRnorm[\calG]{S(f)} 
= \DHJRBignorm[2]{\big(\lambda_i\widehat{f}_i\big)_{i=1}^{N+1}} \\
& \ge \lambda_{N+1} \DHJRBignorm[2]{\big(\widehat{f}_i\big)_{i=1}^{N+1}} = \lambda_{N+1} \DHJRnorm[\calF]{f} = \lambda_{N+1} \rho.
\end{align*}
Thus, $\lambda_{N+1} \le \varepsilon/\rho$, and 
\[
\textup{cost}(A^*,\calB_\rho,\varepsilon) \ge \textup{cost}(A^*,0,\varepsilon)  = N \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \textup{cost}(\widehat{A},\calB_\rho,\varepsilon).
\]
Hence, algorithm $\widehat{A}$ defined in \eqref{optBallalg} is optimal for $\calA(\calB_{\rho})$.

>>>>

To prove this, let $A^*$ be an arbitrary algorithm in $\calA(\calB_{\rho})$, and let $L_1, \ldots, L_N$ be the linear functionals chosen when evaluating this algorithm for the zero function with tolerance $\varepsilon$.  Thus, $A^*(0,\varepsilon)$ is some function of $(L_1(0) , \ldots, L_N(0)) = (0, \ldots, 0)$.  Let $f$ be a linear combination of $u_1, \ldots, u_{N+1}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_N(f) = 0$, then $A^*(\pm f, \varepsilon) = A^*(0, \varepsilon)$, and
\begin{align*}
\varepsilon & \ge \max_{\pm} \DHJRnorm[\calG]{S(\pm f) - A^*(\pm f, \varepsilon)} =  \max_{\pm} \DHJRnorm[\calG]{\pm S( f) - A^*(0, \varepsilon)} \\
& \ge \frac 12 \left [ \DHJRnorm[\calG]{S( f) - A^*(0, \varepsilon)} + \DHJRnorm[\calG]{- S( f) - A^*(0, \varepsilon)}\right] \\
& \ge \DHJRnorm[\calG]{S(f)} 
= \DHJRBignorm[2]{\big(\lambda_i\widehat{f}_i\big)_{i=1}^{N+1}} \\
& \ge \lambda_{N+1} \DHJRBignorm[2]{\big(\widehat{f}_i\big)_{i=1}^{N+1}} = \lambda_{N+1} \DHJRnorm[\calF]{f} = \lambda_{N+1} \rho.
\end{align*}
Thus, $\lambda_{N+1} \le \varepsilon/\rho$, and 
\[
\textup{cost}(A^*,\calB_\rho,\varepsilon) \ge \textup{cost}(A^*,0,\varepsilon)  = N \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \textup{cost}(\widehat{A},\calB_\rho,\varepsilon).
\]
Hence, algorithm $\widehat{A}$ defined in \eqref{optBallalg} is optimal for $\calA(\calB_{\rho})$.
